RNAseq-other studies

### 2018-03-16 datasets/RNA-Seq/RNA-Seq.Rmd
Separated RNA-seq case study vignettes

---
title: "Case Study: RNA-Seq Differential Analysis"
author: "Chinmay Shukla, Patrick Kimes"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: 
    html_document:
        toc: true
        toc_float: true
        highlight: tango
        number_sections: true
---

@@

### Mean Coverage

>>>>

---
title: "Case Study: RNA-Seq Differential Analysis (basal ganglia)"
author: "Chinmay Shukla, Patrick Kimes"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: 
    html_document:
        toc: true
        toc_float: true
        highlight: tango
        number_sections: true
bibliography: bibliography.bib
---

@@

## Mean Counts

### 2018-03-16 datasets/RNA-Seq/RNAseq-Applications.Rmd
Separated RNA-seq case study vignettes

```{r, dat1}
url1 <- download_study('SRP045500')
## Load the data
load(file.path('SRP045500', 'rse_gene.Rdata'))
## Scale counts, may not be needed if using counts directly
dat1 <- scale_counts(rse_gene)
sample_info <- data.frame(run = colData(dat1)$run,
    group = ifelse(grepl('Type 1 Diabetes', as.data.frame(colData(dat1))$characteristics), 'Diabetes', ifelse(grepl('Healthy Control', as.data.frame(colData(dat1))$characteristics),'Healthy','Other')), sequencing_depth = colData(dat1)$reads_downloaded)
## Add sample information for DE analysis
colData(dat1)$group <- sample_info$group

>>>>

```{r, dat1}
url1 <- download_study('SRP045500')
## Load the data
load(file.path('SRP045500', 'rse_gene.Rdata'))
## Scale counts, may not be needed if using counts directly
dat1 <- scale_counts(rse_gene)
sample_info <- data.frame(run = colData(dat1)$run,
    group = ifelse(grepl('Type 1 Diabetes', as.data.frame(colData(dat1))$characteristics), 'Diabetes', ifelse(grepl('Healthy Control', as.data.frame(colData(dat1))$characteristics),'Healthy','Other')), sequencing_depth = colData(dat1)$reads_downloaded)
## Add sample information for DE analysis
colData(dat1)$group <- sample_info$group
ncol(dat1)
```
